---
title: "R Notebook"
output: html_notebook
---

TODO: 
  - implement recording of sui attempts on each tick for agents
  - implement more influential mock intervention?
  - X change id parameter of simulation to sim_id in class definition (not just data export)
  - X remove seed from sim class and data export if it is not going to be used
  - calculate some network statistics ahead of time?
      - assortativity
      - density
      
```{r}
library(tidyverse)

df <- expand.grid(samp = 1:100, net_size = 3:35, person_id = 1:35, baserate = seq(.30, .10, length.out = 10)) %>%
  filter(person_id <= net_size) %>% 
  mutate(beh = as.numeric(runif(n()) < baserate)) %>% 
  group_by(samp, net_size, person_id) %>% 
  summarise(total_beh = sum(beh)) %>% 
  group_by(samp, net_size) %>% 
  mutate(risk_percentile = cume_dist(total_beh))



df
```
    


```{r}
library(tidyverse)
library(dbplyr)

con <- DBI::dbConnect(RSQLite::SQLite(), dbname = 'simulation/test.db')

parameters_db <- tbl(con, 'parameters') %>% 
  select(-id, -tick)

agents_db <- tbl(con, 'agents') %>% 
  rename(agent_id = id) %>% 
  select(-seed)

edges_db <- tbl(con, 'edges')
```


# Question 1 - what is the

```{r}
# Identify individual attempts
agents_db <- agents_db %>% 
  group_by(sim_id, agent_id) %>% 
  mutate(
    attempt = attempt_count - lag(attempt_count, default = 0)) %>% 
  ungroup()

# Partition different periods of the experiment
agents_db <- agents_db %>% 
  left_join(parameters_db, by = 'sim_id') %>% 
  mutate(
    time_period = case_when(
        tick < 100 ~ 'burn_in',
        100 <= tick & tick < 200 ~ 'stabalization',
        200 <= tick & tick < 250 ~ 'baseline',
        250 <= tick & tick < 260 ~ 'active_tx',
        260 <= tick & tick < 310 ~ 'post_tx',
        310 <= tick ~ 'followup'))
```



```{r}
intervention_summary <- agents_db %>% 
  group_by(sim_id, time_period, intv_class_name) %>% 
  summarise(
    attempts = sum(attempt),
    tick = min(tick, na.rm = T),
    n = n(),
    ave_risk = round(50*mean(cur_risk, na.rm = T), 3)) %>% 
  arrange(tick)

intervention_summary
```

```{r}
intervention_effects <- agents_db %>% 
  filter(tick > 100) %>% 
  group_by(intv_class_name, tick) %>% 
  summarise(
    ave_risk = round(50*mean(cur_risk), 3)) %>% 
  ungroup() %>% 
  as_tibble()

ggplot(intervention_effects, aes(x = tick, y = ave_risk, color = intv_class_name)) +
  geom_line()
```



```{r}
baseline_risk <- agents_db %>% 
  filter(time_period == 'baseline') %>% 
  group_by(sim_id) %>% 
  summarise(baseline_risk = mean(cur_risk))




intervention_effects <- agents_db %>% 
  filter(250 < tick) %>% 
  left_join(baseline_risk, by = 'sim_id') %>% 
  group_by(sim_id, time_period, intv_class_name) %>% 
  summarise(rel_change = mean(cur_risk)/baseline_risk) %>% 
  as_tibble()

intervention_means <- intervention_effects %>% 
  group_by(time_period, intv_class_name) %>% 
  summarise(rel_change = mean(rel_change))

head(intervention_effects)
  
ggplot(intervention_effects, aes(time_period, rel_change, color = intv_class_name)) +
  geom_boxplot(position = position_dodge()) +
  geom_point(data = intervention_means, size = 3, position = position_dodge()) +
  theme_bw()
```

```{r}
plot_df <- intervention_effects %>% 
  left_join(baseline_risk, by = 'sim_id') %>% 
  mutate(
    rel_change = round(100*(ave_risk/baseline_risk - 1), 2))

ggplot(plot_df, aes(tick, rel_change, color = intv_class_name)) +
  geom_hline(yintercept = 0, color = 'grey') +
  geom_point() + 
  geom_smooth() +
  theme_bw() +
  theme(panel.grid = element_blank())
```


```{r}
intv_aves <- intervention_effects %>% 
  group_by(time_period, intv_class_name) %>% 
  summarise(ave_risk = mean(ave_risk))

ggplot(intervention_effects, aes(x = time_period, y = ave_risk, color = intv_class_name)) +
  geom_boxplot() + 
  scale_y_continuous(limits = c(0, .10)) +
  geom_jitter(position = position_jitterdodge(), alpha = .250)
```




```{r}
intervention_summary <- agents_db %>% 
  group_by(sim_id, time_period, intv_class_name) %>% 
  summarise(
    attempts = sum(attempt),
    tick = min(tick, na.rm = T),
    n = n(),
    risk = round(50*mean(cur_risk, na.rm = T), 3)) %>% 
  arrange(tick)


intervention_effect <- intervention_summary %>% 
  ungroup() %>% 
  select(tick, time_period, intv_class_name, risk) %>% 
  pivot_wider(
    id_cols = c(intv_class_name),
    names_from = time_period,
    values_from = risk) %>% 
  as_tibble()


intervention_effect %>% 
  mutate(
    active_effect = active_tx - baseline,
    post_effect = post_tx - baseline,
    followup_effect = followup - baseline) %>% 
  select(intv_class_name, ends_with('effect')) %>% 
  pivot_longer(
    cols = ends_with('effect'),
    names_to = 'metric',
    values_to = 'magnitude') %>% 
  pivot_wider(
    names_from = 'intv_class_name',
    values_from = 'magnitude')


```

```{r}
plot_df <- agents_db %>% 
  filter(tick > 0) %>% 
  group_by(sim_id, tick, intv_class_name) %>% 
  summarise(
    attempts = mean(attempt, na.rm = T),
    n = n(),
    risk = 50*mean(cur_risk, na.rm = T)) %>% 
  arrange(tick)

plot_df

ggplot(plot_df, aes(tick, risk, group = sim_id, color = intv_class_name)) +
  geom_line(alpha = .10) +
  scale_y_continuous(limits = c(0, .02))
```


```{r}
DBI::dbDisconnect(con)
```



